---
title: "STAT 6210 - Homework 4"
author: "Ana Gabriela Itokazu"
date: "due date: Oct 30, 2020"
output:
     prettydoc::html_pretty:
          theme: tactile
          highlight: github
---

```{r chunksetup, include=FALSE}
knitr::opts_chunk$set(
   echo=TRUE, eval=TRUE, include=TRUE,
   warning=FALSE, message=FALSE,
   fig.align="center"
)
```

```{r clear_genv, echo=FALSE}
rm(list = ls())
library(tidyverse)
library(knitr)
```

```{css, echo=FALSE}
 
     .image {
          display: block;
          margin-left: auto;
          margin-right: auto;
          width: 90%;
}

     .textbox {
          padding: 1em;
          background: lightgrey;
}
```

<div style="text-align: center">

Final `.html` file knitted in October 30, 2020 (source code available in [Github](https://github.com/AU-R-Programming/HW4-Gabii)).

</div>

***

<div style="text-align: justify">

### Royal Blood:

I could make it work with ifelse's in a function:

</div>

```{r royal1, results = FALSE}

blob <- function(a){
     print(ifelse(a%%3==0 && a%%5==0, "Royal Blood",
                  ifelse(a%%3==0, "Royal",
                         ifelse(a%%5==0, "Blood", a))))
}

blub <- Vectorize(blob)
q1 <- blub(1:1000)

```

Or in a for loop using the same logic:

```{r royal2, eval=FALSE}

for (a in seq(1000)) {
     if (a%%3==0 && a%%5==0) {
          print("Royal Blood")
     } else if (a%%3==0){
          print("Royal")
     } else if (a%%5==0){
          print("Blood")
     } else
          print(a)
}
```

Then we'll get something like this:

<div class="textbox" id="royalbloodshow">

`r q1[1:35]`, ...

</div>

<div style="text-align: justify">

\

### Let's get things in order:

</div>

```{r order, eval=FALSE}

for (i in (1:length(a))) {
     for (j in (1:(length(a)-1))) {
          if (a[j] > a[j+1]) {
               swap(a[j], a[j+1])
          }
     }
}

``` 


With that, if I provide a vector *a = c(9,5,2,6,3,-9,4,5,-6,2,8,34,89,6)* as an input, it will turn out as *a = c(-9,-6,2,2,3,4,5,5,6,6,8,9,34,89)* afterwards!!

<div style="text-align: justify">

\

### To the bare minimum:

</div>

```{r q4}

f <- function(x) x^2 - 2*x + 1
threshold<- .Machine$double.eps^0.25
delta <- 0
x1 = -1
x3 = 3
set.seed(123)
x2 = runif(1, x1, x3)

i <- c(x1, x2, x3)
i1 <- c(0, 0, 0)

while(delta > threshold || delta == 0){

        if((i[2]-i[1]) > (i[3] - i[2])){

                x4 <- runif(1, i[1], i[2])

                if((f(x4) < f(i[2]))){
                        i1 <- c(i[1], x4, i[2])
                } else {
                        i1 <- c(x4, i[2], i[3])
                }
        } else {
                x4 <- runif(1, i[2], i[3])

                if((f(x4) < f(i[2]))){
                        i1 <- c(i[2], x4, i[3])
                } else {
                        i1 <- c(i[1], i[2], x4)
                }
        }

        delta <- abs(f(i[2]) - f(i1[2]))

        i = i1
}

print(c(i1[2],f(i1[2])))

```

.. And the values printed above are the central point in the last triplet (\(i(n),x_2\)) and its respective function value (\(f(x_2)\)).


<div class="textbox" id="minumumcomment">

I'm sorry I made you feel like you didn't explained well enough.! I had a hard time getting this homework done because of my own individual things, not because of the class, or you. I'm sorry if I gave out the wrong impression.!

</div>



